% Version: $Revision$

\begin{thebibliography}{999}
	% to make the bibliography appear in the TOC
	\addcontentsline{toc}{chapter}{Bibliography}

	\bibitem{kepler}
		\textit{Kepler} -- A free and open source, scientific workflow application. \\
		\url{https://kepler-project.org/}{}

	\bibitem{keplerweka}
		\textit{KeplerWeka} -- A module for the Kepler workflow engine, which adds
		WEKA functionality. \\
		\url{http://keplerweka.sourceforge.net/}{}

	\bibitem{adams}
		\textit{ADAMS} -- Reutemann, Peter and Vanschoren, Joaquin (2012).
		\textit{Scientific Workflow Management with ADAMS}. Proceedings
		of the Machine Learning and Knowledge Discovery in Databases
		(ECML-PKDD), Part II, LNCS 7524, pp. 833–837. \\
		\url{https://adams.cms.waikato.ac.nz/}{}

	\bibitem{git}
		\textit{Git} -- a free and open source distributed version
		control system designed to handle everything from small to
		very large projects with speed and efficiency. \\
		\url{https://git-scm.com/}{}

	\bibitem{github}
		\textit{GitHub} -- One of the largest public platforms hosting
		git repositories, open-source and business alike. \\
		\url{https://github.com/}{}

	\bibitem{maven}
		\textit{Apache Maven} -- Software project management and comprehension tool.
		\\
		\url{http://maven.apache.org/}{}

	\bibitem{nexus}
		\textit{Nexus} -- Repository manager for Apache Maven. \\
		\url{http://nexus.sonatype.org/}{}

	\bibitem{intellij}
		\textit{IntelliJ IDEA} -- Even the community edition of IntelliJ IDEA
		is a powerful environment for development Java projects. \\
		\url{https://www.jetbrains.com/idea/}{}

	\bibitem{eclipse}
		\textit{Eclipse} -- An open development platform comprised of extensible
		frameworks, tools and runtimes for building, deploying and managing
		software across the lifecycle. \\
		\url{http://eclipse.org/}{}

	\bibitem{junit}
		\textit{JUnit} -- JUnit is a unit testing framework for the Java
		programming language. \\
		\url{http://junit.org/}{}
		
	\bibitem{dateformat}
		\textit{DateFormat} -- For parsing date/time strings and turning date/time
		objects into strings.
		\url{http://download.oracle.com/javase/1.5.0/docs/api/java/text/DateFormat.html}{}
		
	\bibitem{regexp}
		\textit{Regular expressions} -- The regular expression handling as available
		in Java.
		\url{http://download.oracle.com/javase/1.6.0/docs/api/java/util/regex/Pattern.html}{}

	\bibitem{json}
		\textit{JSON} -- JavaScript Object Notation.
		\url{http://json.org/}{}

	\bibitem{yaml}
		\textit{YAML} -- YAML Ain't Markup Language, a human friendly
		data serialization standard for all programming languages.
		\url{http://yaml.org/}{}

	\bibitem{nssm}
		\textit{NSSM} -- The Non-Sucking Service Manager.
		\url{http://nssm.cc/}{}

\end{thebibliography}
